Dac summary 01/19/2021

### 2022-06-23 msdepression/scripts/Group_level_analyses/msdepression_regressions_started_20211118.Rmd
afni command to make yeo networks

dep_vs_healthy <- lmerTest::lmer(total_fascicle_prop_lost ~ depGroupVar + (1 | EMPI) + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_easy <- lm(total_fascicle_prop_lost ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_vs_healthy_net <- lmerTest::lmer(total_fascicle_prop_lost_indepnet ~ depGroupVar + (1 | EMPI) + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_easy_dep_net <- lm(total_fascicle_prop_lost_indepnet ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_vs_healthy_net_10_percent <- lmerTest::lmer(total_fascicle_prop_lost_indepnet_10_percent ~ depGroupVar + (1 | EMPI) + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_easy_dep_net_10_percent <- lm(total_fascicle_prop_lost_indepnet_10_percent ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

@@

>>>>

dep_vs_healthy <- lmerTest::lmer(total_fascicle_prop_lost ~ depGroupVar + (1 | EMPI) + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis) #trend, p = 0.15

#dep_easy <- lm(total_fascicle_prop_lost ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_vs_healthy_net <- lmerTest::lmer(total_fascicle_prop_lost_indepnet ~ depGroupVar + (1 | EMPI) + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis) #trend, p = 0.14

#dep_easy_dep_net <- lm(total_fascicle_prop_lost_indepnet ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

dep_vs_healthy_net_10_percent <- lmerTest::lmer(total_fascicle_prop_lost_indepnet_10_percent ~ depGroupVar + (1 | EMPI) + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis) #p = 0.23

#dep_easy_dep_net_10_percent <- lm(total_fascicle_prop_lost_indepnet_10_percent ~ depGroupVar + PAT_AGE_AT_EXAM, data = dep_and_healthy_groups_for_ICD_analysis)

@@

#anova
fascicle_agedep_anova <- lapply(fascicle_agedep_lm, anova) #p unc= C_PH_L, p = 0.03, PAT_R p=0.04, slf1_R p = 0.09, VOF_R p = 0.03

### 2022-06-23 msdepression/scripts/K23_prelim_data_started_20220225.Rmd
afni command to make yeo networks

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Fascicle <- rep(c("Depression Network (AF)" , "Non-depression network (SCP)"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]),
           mean(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))),
          (sd(dep_and_healthy_groups_for_ICD_analysis$SCP[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))))

@@

barplot2 <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
    geom_bar(position="dodge", stat="identity", colour = "black", width=0.9,size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) + 
    scale_fill_manual(values = c("#cdcdcd", "#FFFFFF", "#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph

@@

>>>>

Diagnosis <- c(rep("Depressed" , 2) , rep("Non-Depressed" , 2))
Fascicle <- rep(c("Depression Network (AF)" , "Region Outside Depression Network (C_PH)"), 2)
value <- c(mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2]),
           mean(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]),
           mean(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1]))

sem <- c((sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 2])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==2))),
           (sd(dep_and_healthy_groups_for_ICD_analysis$AF_R[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))),
          (sd(dep_and_healthy_groups_for_ICD_analysis$C_PH_L[dep_and_healthy_groups_for_ICD_analysis$depGroupVar == 1])/sqrt(sum(dep_and_healthy_groups_for_ICD_analysis$depGroupVar ==1 ))))

@@

barplot2 <- ggplot(data, aes(fill=Diagnosis, y=value, x=Fascicle)) + 
    geom_bar(position="dodge", stat="identity", colour = "black", width=0.9,size=1.5) + 
    geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1) + 
    scale_fill_manual(values = c("#cdcdcd", "#FFFFFF", "#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph

@@

print(barplot)
# Black and white
barplot <- ggplot(data, aes(x=Network,fill=Network, y=value)) + 
  geom_bar(stat="identity", colour="black", width=0.8, size=1.5) + 
  geom_errorbar(aes(ymin=value-sem, ymax=value+sem), width=.1, position=position_dodge(0.9), size=1.5) +
  scale_fill_manual(values = c("#cdcdcd", "#FFFFFF")) + #comment out if you want colored graph
  ylab("Proportion of Fascicles Affected") +
  theme(axis.text = element_text(size = 14, colour = "black"), axis.title.x = element_blank(), 
        axis.title.y = element_text(size=20),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        panel.background = element_rect(colour = "white", fill = "white")) + #comment out if you want pretty 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.52)) #comment out if you want colored graph

### 2022-06-23 msdepression/scripts/dac_summary.Rmd
afni command to make yeo networks

#obtained from: unique(data_empi_acc_f_phq$Provider[grep("PRUIT", data_empi_acc_f_phq$Provider)])
ms_providers <- c("MARKOWITZ, CLYDE E.", "JACOBS, LINDA", "WILLIAMSON, ERIC MICHAEL-LEE", "BERGER, JOSEPH ROBERT", "BERGER DO, JOSEPH", "PRUITT, AMY A.", "KOLSON, DENNIS L.", "CHAHIN, SALIM", "NARULA, SONA", "BAR-OR, AMIT")

@@

data_e <- data4_20210119[which(data_empi_acc_f_phq$Provider %in% ms_providers),]
dep_df <- grep("F3", data_e$ICD10)
unique_empi <- which(unique(data_e$EMPI) %in% data_e$EMPI) #index of the locations of unique empis
num_unique_EMPI_and_dep <- sum(unique_empi %in% dep_df) #n = 469

>>>>

#obtained from: unique(data_empi_acc_f_phq$Provider[grep("PRUIT", data_empi_acc_f_phq$Provider)])
ms_providers <- c("MARKOWITZ, CLYDE E.", "JACOBS, DINA A.", "WILLIAMSON, ERIC MICHAEL-LEE", "BERGER, JOSEPH ROBERT", "BERGER DO, JOSEPH", "PRUITT, AMY A.", "KOLSON, DENNIS L.", "CHAHIN, SALIM", "NARULA, SONA", "BAR-OR, AMIT")

@@

data_e <- data4_20210119[which(data4_20210119$Provider %in% ms_providers),]

dep_df <- grep("F3", data_e$ICD10)
unique_empi <- which(unique(data_e$EMPI) %in% data_e$EMPI) #index of the locations of unique empis
num_unique_EMPI_and_dep <- sum(unique_empi %in% dep_df) #n = 469

### 2022-06-23 msdepression/scripts/final_dac_summary_pull_20210119.Rmd
afni command to make yeo networks

@@

melissa_qc_data <- read.csv("/Users/eballer/BBL/msdepression/data/dac/just_empi_date_rating", sep = ",", header = F) #n = 2841
names(melissa_qc_data) <- c("EMPI", "EXAM_DATE", "rating")
subset_with_qc <- merge(subset, melissa_qi_data, by = c("EMPI", "EXAM_DATE"))

write.csv(subset_with_qc, "/Users/eballer/BBL/msdepression/data/dac/subset_with_qc_for_tim_20211117.csv", col.names = T)

>>>>

print("Get people in healthy group with phq9s for dep/healthy")
# num in healthy group with PHQ9
phq9_subset <- healthy_df[which(!is.na(healthy_df$PHQ.9)),] #n=121
depressed_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 >= 10),] #n = 32 
depressed_unique_phq9_empis <- unique(depressed_phq9_subset$EMPI) #n=9
healthy_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 == 0),] #n = 21
healthy_unique_phq9_empis <- unique(healthy_phq9_subset$EMPI) #n =4
healthyish_phq9_subset <- phq9_subset[which(phq9_subset$PHQ.9 <= 4),] #n = 55
healthyish_unique_phq9_empis <- unique(healthyish_phq9_subset$EMPI) #n =9

@@

melissa_qc_data <- read.csv("/Users/eballer/BBL/msdepression/data/dac/just_empi_date_rating", sep = ",", header = F) #n = 2841
names(melissa_qc_data) <- c("EMPI", "EXAM_DATE", "rating")

bad_flairs <- read.csv("/Users/eballer/BBL/msdepression/data/dac/missing_flair.csv", sep = ",", header = T) #n = 1561
bad_flairs$EXAM_DATE <- gsub(pattern = "-", replacement = "", x = bad_flairs$date)

subset_with_qc <- merge(subset, melissa_qi_data, by = c("EMPI", "EXAM_DATE"))
subset_excluded <- merge(subset, bad_flairs, by = c("EMPI", "EXAM_DATE")) #n = 1973;  healthy = 457, uncategorized = 1284, depressed = 232

unique <- subset_excluded %>% 
  group_by(EMPI) %>% 
  arrange(EXAM_DATE) %>% 
  slice(1) %>% 
  ungroup()  #n (total) = 458, healthy = 114, uncat = 282. dep = 62

write.csv(subset_with_qc, "/Users/eballer/BBL/msdepression/data/dac/subset_with_qc_for_tim_20211117.csv", col.names = T)
write.csv(subset_with_qc, "/Users/eballer/BBL/msdepression/data/dac/subset_bad_flairs_for_tim_20211117.csv", col.names = T)
